### 2020-07-05 chapters/conclusions.tex
Correct wassertein vs jsd example

In this thesis, we used the Jensen–Shannon Divergence (JSD) as a statistical test to measure the distance or divergence between our reference and target sliding window aggregation. We chose to use the JSD metric due to its simplicity and because it was used in previous work successfully \cite{SAMM}. We believe that future work comprises testing new distances in the literature. In particular, we believe the Wasserstein distance is worth trying next, and illustrate why in Figure \ref{fig:wasserteinvsjsd}.
\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.6]{figures/wasserstein-vs-jsd.pdf}
      \caption{Wassertein vs Jensen–Shannon distances}
      \label{fig:wasserteinvsjsd}
    \end{center}
\end{figure}
The Wasserstein distance measures the work required to transport the probability mass from one histogram to the other. This measure will be larger the further way the probability mass is. In Figure \ref{fig:wasserteinvsjsd} scenario, while in the JSD measure is the same for both cases, the Wasserstein distance is larger in case 2 because the probability mass has to be transported further.

>>>>

In this thesis, we used the Jensen–Shannon Divergence (JSD) as a statistical test to measure the distance or divergence between our reference and target sliding window aggregation. We chose to use the JSD metric due to its simplicity and because it was used in previous work successfully \cite{SAMM}. We believe that future work comprises testing new distances in the literature. In particular, we believe the Wasserstein distance is worth trying next, and illustrate why with Figure \ref{fig:wasserteinvsjsd} and Table \ref{tbl:wassertein-vs-jsd}. 
\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.55]{figures/wasserstein-vs-jsd.pdf}
      \caption{Wassertein vs Jensen–Shannon distances}
      \label{fig:wasserteinvsjsd}
    \end{center}
\end{figure}
\begin{table}[!htb]
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
        \hline
        \textbf{Distribution \#1} & \textbf{Distribution \#2} & \textbf{Wasserstein Output} & \textbf{Jensen–Shannon Output} \\ \hline
        a                         & a'                        & 2.0                         & 0.4451                         \\ \hline
        b                         & b'                        & 0.5                         & 0.4451                         \\ \hline
        \end{tabular}
    \end{center}
    \caption[Wasserstein and Jensen-Shannon divergences output comparison]{Wasserstein and Jensen-Shannon divergences for both distribution pairs}
    \label{tbl:wassertein-vs-jsd}
\end{table}
The Wasserstein distance measures the work required to transport the probability mass from one histogram to another. This measure will be larger the further way the probability mass is. In Figure \ref{fig:wasserteinvsjsd}, we show two pairs of histograms, \textit{Histogram (a)} paired with \textit{Histogram (a')} and \textit{Histogram (b)} paired with \textit{Histogram (b')}. Table \ref{tbl:wassertein-vs-jsd} shows the output values for both pairs by each divergence function. The JSD measure is the same for both cases, whereas the Wasserstein distance is larger for the first pair because the probability mass has to be transported further.

### 2020-07-05 chapters/resumo.tex
Correct wassertein vs jsd example

%Approach/Solution and %Main contributions
Nesta tese, projetamos um método que utiliza agregações de \textit{streaming} leves e funções de divergência de distribuição para alertar sobre desvios nos padrões de dados em tempo real, na presença de grandes volumes de dados a alta velocidade, distorcidos e sazonais. Desenvolvemos um método de duas fases e duas janelas: primeiro, realizamos uma análise \textit{batch} numa janela de referência e, em seguida, uma análise \textit{streaming} sobre uma janela deslizante. Agregamos o conteúdo de ambas as janelas usando um histograma aproximado baseado em Médias Móveis Exponenciais (MMEs). Fazemos isto para cada evento e cada um dos seus campos, também denominados \textit{features} no nosso contexto. Medimos a divergência entre os histogramas de referência e os das janelas deslizantes baseados em MMEs para cada \textit{feature} com a função de divergência de \textit{Jensen-Shannon}, mas outras funções podem ser usadas. Para cada \textit{feature}, descobrimos o valor de probabilidade para cada medida de divergência e aplicamos a correção de múltiplo teste de Holm-Bonferroni para descobrir quais os valores de probabilidade mais baixos e as \textit{features} associados. Geramos alertas  para cada \textit{feature} com base num limite de probabilidade definido pelo administrador.

@@

\vspace*{10mm}\noindent
\textbf{Keywords}: data streams, monitoring, real-time, lightweight, concept drift

>>>>

%Approach/Solution and %Main contributions
Nesta tese, projetamos um método que utiliza agregações de \textit{streaming} leves e funções de divergência para alertar sobre desvios nos padrões de dados em tempo real, na presença de grandes volumes de dados que fluem a alta velocidade, são altamente \textit{skewed} e sazonais. Desenvolvemos um método de duas fases e duas janelas: primeiro, realizamos uma análise \textit{batch} numa janela de referência e, em seguida, uma análise \textit{streaming} sobre uma janela deslizante. Agregamos o conteúdo de ambas as janelas usando um histograma aproximado baseado em Médias Móveis Exponenciais (MMEs). Fazemos isto para cada evento e cada um dos seus campos, também denominados \textit{features} no nosso contexto. Medimos a divergência entre os histogramas de referência e os das janelas deslizantes baseados em MMEs para cada \textit{feature} com a função de divergência de \textit{Jensen-Shannon}, mas outras funções podem ser usadas. Para cada \textit{feature}, descobrimos o valor de probabilidade para cada medida de divergência e aplicamos a correção de múltiplo teste de Holm-Bonferroni para descobrir quais os valores de probabilidade mais baixos e as \textit{features} associados. Geramos alertas  para cada \textit{feature} com base num limite de probabilidade definido pelo administrador.

@@
